Verifying Spatial Properties of Array Computations

### 2017-04-14 oopsla17/oopsla17.tex
describing our methodology

\usepackage{hyperref}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{syntax}
\usepackage{indentfirst}
\usepackage{cleveref}
\usepackage{xcolor}
\usepackage{siunitx} % For pretty-printing numeric values and SI units
                     % of measure. e.g., the tabular column type S is
                     % used to print nice-looking tables of numbers.
\sisetup{ % defaults
  group-separator={,},
  group-minimum-digits={3},
  output-decimal-marker={.},
  table-format = 6
}

\usepackage{minted}
\usepackage{etoolbox}

\usepackage{thmtools}
\usepackage{thm-restate}

@@

\section{An Empirical Study of Array Computations in Scientific Fortran code}

\begin{enumerate}
\item Stencils are ubiquitious;
\item Most stencils read their data from source arrays with a static pattern
base on constant offsets from the mid-point;
\item Most stencils read their data from contiguous \emph{regions} in an array;
\item Most stencils read each index at most once.
\end{enumerate}

\subsection{Study}
%
\noindent
We put together a corpus of around 1 million lines of Fortran code from a
\numPackages{} scientific computing packages ranging in size and scope: The Unified Model (UM)~\cite{um},
E3MG~\cite{RePEc:aen:journl:2006se-a12}, BLAS~\cite{blas},
Hybrid4~\cite{GBC:GBC635}, GEOS-Chem~\cite{geos-chem}, Navier (based
on \cite{griebel1997numerical}), Computational Physics
2~\cite{nicholas2006computational},
ARPACK-NG~\cite{arpackng}, and
SPECFEM3D~\cite{specfem3d}. Appendix~\ref{app:corpus} provides
further detail on these packages.

We used Wheeler's \emph{SLOCCount} to get a count of the physical
source lines (excluding comments and blank
lines)~\cite{wheeler2001sloccount}; including non-physical lines
 our corpus totals \dnote{insert}.

\begin{itemize}
% (Vars, ...)
\item An assignment to a variable, with an RHS comprising some array
  computation, tends to correspond to a reduction (e.g., calculating
the max value in an array).

\end{itemize}

>>>>

\usepackage{hyperref}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{syntax}
\usepackage{indentfirst}
\usepackage{cleveref}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{siunitx} % For pretty-printing numeric values and SI units
                     % of measure. e.g., the tabular column type S is
                     % used to print nice-looking tables of numbers.
\sisetup{ % defaults
  group-separator={,},
  group-minimum-digits={3},
  output-decimal-marker={.},
  table-format = 6
}

\usepackage{minted}
\usepackage{etoolbox}
\usepackage{enumitem}
\usepackage{thmtools}
\usepackage{thm-restate}

\newcommand{\fortran}[1]{\mintinline{fortran}{#1}}

@@

\section{An Empirical Study of Array Computations in Scientific Fortran code}
\label{sec:study}
\input{study}
